\bf The Right Arm Bias in ITF Taekwon-Do \\ Patterns Chon-Ji to Juche

### 2012-02-24 article.tex
Added conclusions
Readded figures for color belt and black belt patterns

  With a few exceptions, all techniques by all patterns for both sides, follow
  the same trend, where there are most blocks, then there are more punches
  than strikes, and more strikes than thrusts (Figure \ref{fig:patterns_all}).

@@

  The exceptions for all techniques on both sides are: Chon-Ji (having more
  blocks than punches), Choong-Moo, Choong-Jang and Juche (with more punches
  than strikes) and Po-Eun (where there are more strikes than thrusts).

@@

%\Section{Conclusions}

%What are the implications of your answer? Is it going to change the
%world (unlikely), be a significant ``win'', be a nice hack, or simply
%serve as a road sign indicating that this path is a waste of time (all
%of the previous results are useful). Are your results general,
%potentially generalizable, or specific to a particular case?

% Is it possible to say anything about why there are more techniques with the
% right hand, than with the left?

% Observation: Kicks happen between stances

>>>>

  With a few exceptions, all techniques by all patterns for both sides, follow
  the same trend, where there are most blocks, then there are more punches
  than strikes, and more strikes than thrusts (Figure \ref{fig:patterns_all}).
  This trend is also true when grouping the patterns by black belt patterns
  and color belt patterns (Figures \ref{fig:patterns_black_all},
  \ref{fig:patterns_color_all}).

@@

  % all techniques by black belt patterns
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_black_all}
    \caption{All techniques by black belt patterns.}
    \label{fig:patterns_black_all}
  \end{figure}

  % all techniques by color belt patterns
  \begin{figure}
    \includegraphics[scale=0.72]{data/gnuplot/eps/patterns_color_all}
    \caption{All techniques by color belt patterns.}
    \label{fig:patterns_color_all}
  \end{figure}

  The exceptions for all techniques on both sides are: Chon-Ji (having more
  punches than blocks ), Choong-Moo, Choong-Jang and Juche (with more strikes
  than punches) and Po-Eun (where there are more thrusts than strikes).

@@

\Section{Conclusions}

  There are more hand techniques performed on the right side than on the left
  side. Thusly, there is a bias towards the right side.
